Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-28 paper/paper.tex
fix a typo
more fixes

Defining a language by building an interpreter for it can be traced to the very
early days of programming languages research \cite{McCarthy:1960:RFS:367177.367199,landin1966next, Reynolds:72}.
Nowadays, even undergraduate students in computer science learn how to make their own
programming languages by building an interpreter.
But building a sound abstract interpreter remained an esoteric and difficult task 
until very recently.

@@

We begin by reviewing some background necessary for this work in Section~\ref{background}, 
as well as introducing some of the basic code structures used throughout the paper. 
We then address the main contribution of this paper: bridging the gap between
small-step AAM and big-step ADI by applying a series of well-known systematic transformations
drawn from concrete semantic artifacts.
Those transformations are shown in Figure~\ref{fig:trans} and summarized here, with their 
respective associated sections:

@@

We complete this paper by discussing related work in Section~\ref{sec:related}, followed by 
concluding thoughts in Section~\ref{sec:conclusion}.

@@

\textit{Defunctionalization and Refunctionalization.}
Defunctionalization and refunctionalization build connections between abstract machines and
interpreters. \citeauthor{Reynolds:72} first shows defunctionalization as a program transformation 
technique that can be used to transform higher-order functions to first-order functions when
writing a definitional interpreter \cite{Reynolds:72, Reynolds:HOSC98-revisited}.
Refunctionalization is a left inverse of this transformation.

@@

We show the functional correspondence not only exists between concrete semantic artifacts
but also exists between abstract semantic artifacts. An interesting open question would
be whether there also exists correspondences between static analyses that are formalized 
in different denotational and operational styles.

>>>>

Defining a language by building an interpreter for it can be traced to the very
early days of programming languages research \cite{McCarthy:1960:RFS:367177.367199,landin1966next, Reynolds:72}.
Nowadays, even undergraduate students in computer science learn how to define 
their own programming languages by building an interpreter.
But building a sound abstract interpreter remained an esoteric and difficult task 
until very recently.

@@

We begin by reviewing some background necessary for this work in Section~\ref{background}, 
as well as introducing some of the basic code structures used throughout the paper. 
We then address the main contribution of this paper: bridging the gap between
small-step AAM and big-step ADI by applying a series of well-known systematic transformations
drawn from concrete semantic artifacts.
Those transformations are shown in Figure~\ref{fig:trans} and summarized here, with full
descriptions in their respective associated sections:

@@

We discuss related work in Section~\ref{sec:related}, followed by 
concluding thoughts in Section~\ref{sec:conclusion}.

@@

\textit{Defunctionalization and Refunctionalization.}
Defunctionalization and refunctionalization build connections between abstract machines and
interpreters. \citeauthor{Reynolds:72} first shows defunctionalization as a program transformation 
technique that can be used to transform higher-order functions to first-order functions when
writing a definitional interpreter \cite{Reynolds:72, Reynolds:HOSC98-revisited}.
Refunctionalization~\cite{TODOrefunc} is the left inverse of this transformation.

@@

We show that a functional correspondence exists not only between concrete semantic artifacts
but also between abstract semantic artifacts. An interesting open question would
be whether there also exist correspondences between static analyses that are formalized 
in different denotational and operational styles.
